Draft

### 2020-02-20 SubGroup.Rmd
subgroup changes

## Subgroup Curves
```{r subgroup curves, eval=F}
# subgroup 4 curves
SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
SubgroupPlot <- SubgroupPlot[, -1]
SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
SubgroupPlotOrigin <- SubgroupPlot

>>>>

## Subgroup Curves
```{r subgroup curves, eval=F}
# subgroup 4 curves
SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
SubgroupPlot <- SubgroupPlot[, -1]
SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
SubgroupPlotOrigin <- SubgroupPlot
SubgroupPlot <- SubgroupPlotOrigin
SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)

SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.Without prior TB history"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.With prior TB history"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young [15,25)"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
# SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% ""] <-
# SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% ""] <-
SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)
